Verifying Demonstrations

### 2020-03-13 paper/DB-Schnorr-UWB.tex
Fixes refs, nbit MF thm

\section{Distance-bounding \aclp*{ZKPK} for discrete logarithms}%
\label{DB-Schnorr-UWB}

@@

We also deviate from the normal technique of one-bit challenges and responses 
otherwise used in \ac{DB} protocols.
\Textcite{UWBPR} proposed a secure encoding for the physical 
layer which removes the requirement of only using single-bit challenges and 
responses for distance bounding.
However, their protocol only works for relay attacks and cannot handle distance 
fraud.
This is due to a requirement of the protocol that the prover and verifier must 
share a secret, and thus must be mutually trusted.

We will first present our version of the \ac{DB} Schnorr protocol for the 
mutual-trust case, where the prover and verifier have a pre-shared secret.
Then we will adapt it by introducing \iac{PKI}.
We will use this \ac{PKI} to create \iac{AKE} which leverages that our protocol 
is \iac{DB} \ac{ZKPK} for discrete logarithms.
If the \ac{PKI} is based on discrete logarithms we can prove the distance bound 
while we authenticate the key.
This turns the mutual-trust by shared-key into mutual trust by 
\ac{PKI}.

\subsection{Reattempting a distance-bounding Schnorr protocol}%
\label{DB-Schnorr}

Thanks to \textcite{UWBPR} we can keep the Schnorr protocol almost as is, since 
relays (\ac{DBMF}, \ac{DBDH}) are dealt with on the physical layer.
\Ac{DBDF} is not a concern either, since the prover is trusted.
The only concern, for now, is \acl{DBTF}.
(However, we will still prove those properties, as they will be useful later.)

We present the protocol in \cref{DB-Schnorr-UWB-figure}.
The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.
Let \(\UWBPR\) be the protocol of \textcite{UWBPR}.
Further, let
\(\UWBPRsend[_k][m]\) denote sending a message~\(m\) with the shared key~\(k\),
\(m'\gets \UWBPRrecv_k\) denote receiving a message~\(m'\) with shared 
key~\(k\) and finally
\(\Delta t\gets \UWBPRtime\) denote the time between the last \(\UWBPRsend\) 
and \(\UWBPRrecv\) operations.

\begin{figure*}
  \centering
  \small
  \setlength{\ProtoArrowLength}{0.07\linewidth}
  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
    \(\DBSprove[k, g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[k, g, q, A]\):
    \\
    \midrule

@@

    Load \(k\) into \(\UWBPR\)
    &
    & Load \(k\) into \(\UWBPR\)
    \\

@@

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
    protocol instantiating \(\PK[\alpha][A = g^\alpha]\).
    Each transmission (arrow in the diagram) uses \(\UWBPR\).
    The protocol should be repeated \(n\) times to achieve the desired 
    soundness and distance-bounding errors.
  }%
  \label{DB-Schnorr-UWB-figure}
\end{figure*}

@@

The intuition behind the protocol security is as follows.
The prover must know the responses for all challenges to successfully pass the 
\ac{DB} phase.
The reason for having several challenges but only one random nonce is that 
knowing at least two responses means learning the secret~\(\alpha\).
This gives us the incentives that prevent \ac{DBTF}.
(We also need it for \ac{DBMF}.)
Bundling the authentication into the distance-bounding phase (difference from 
Brands-Chaum) prevents \ac{DBDH}.
We do not consider \ac{DBDF} here; since the prover knows the key~\(\sk\), she 
can do \iac{DBEDLC} attack to reduce the distance.
(We will solve this problem further down.)
However, the properties of \(\UWBPR\) and the unpredictability of the 
challenges ensures \ac{DBMF} resistance (since then the prover is honest).

@@

The \(\UWBPR\) prevents \iac{DBMF} adversary from performing a 
distance-reduction through \iac{DBEDLC} attack~\cite{UWBPR}.
Thus, any relaying will be detected, \ie this justifies \cref{TaintedMF}.

\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \frac{1}{m^n}\), where \(m\) is as in 
  \cref{DB-Schnorr}.
\end{theorem}

@@

The protocol is \ac{DBTF} resistant.
Indeed, if the malicious prover gives more than one response to the accomplice, 
the accomplice can compute the secret key and, thus, impersonate forever.
And any help will increase the probability of success of future attempts.

@@

\subsection{From mutual trust to \acs*{PKI}}

All \acl{DB} protocols requires hardware 
implementations~\cite{DBonSmartphones}.
We will use a \emph{trusted} hardware implementation to overcome the limitation 
of \textcite{UWBPR}, \ie that the prover and verifier must be mutually trusted.
We will need \iac{PKI} for the verifier to verify the trusted hardware.
We will leverage this \ac{PKI} to overcome the shared-key requirement to allow 
any two devices in this \ac{PKI} to perform \acl{DB}.
With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
\ac{ZKPK} which \emph{simultaneously} proves
\begin{enumerate*}
\item that the protocol is run by trusted hardware,
\item that that trusted hardware is within proximity,
\item that some \ac{ZKPK} statement about some discrete logarithms holds, and
\item that that knowledge is within proximity.
\end{enumerate*}

We will now introduce an extended protocol, \(\DBSHW\), which represents the 
secure hardware implementation.
\Cref{DBSHW-overview} presents an overview of our protocol.
For simplicity of exposition, we present a \ac{PKI} based on plain 
CL04~\cite{CLsignatures} signatures.
However, CL04 is the base for the \ac{DAA} protocol, which is used for 
\ac{TPM}, so our protocol can be modified into \iacl{DB} \ac{DAA} protocol.

In summary, the difference is as follows.
\(\DBS\) has a static shared key~\(k\) and performs \(
  \PK[\alpha][A = g^\alpha]
\) with a distance bound.
\(\DBSHW\) first runs \iac{DHKE} to establish the shared key~\(k =
\gDH^{\xDH \yDH}\) from \(\XDH = \gDH^{\xDH}, \YDH = \gDH^{\yDH}\), then 
performs \[
  \PK[\alpha, \xDH, \sk_P, \sigma][
    A = g^\alpha \land
    \XDH = \gDH^{\xDH} \land
    \XDHCL = \XDH^{\sk} \land
    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
  ],
\] also with a distance bound; where \(\sk_P\) is the prover's private key, 
\(\sigma\) is a signature issued with signing key~\(\sk\) and \(\Blind\) 
reblinds a signature.
Proving knowledge of \(\XDH = \gDH^{\xDH}\) and \(\XDHCL = \XDH^{\sk}\) 
prevents any \ac{MITM} attack against the \ac{DHKE}.
Proving knowledge of a signature~\(\sigma\) by \iac{CA} on the private 
key~\(\sk_P\) ensures that the prover is a device in the \ac{PKI} of the 
\ac{CA}.

\Cref{DBSHW-overview} provides an overview.
For simplicity of the exposition, we present a version of \(\DBSHW\) that 
allows the user to run \(\PK[\alpha][A = g^\alpha]\) (the Schnorr 
identification scheme) with a distance bound.
This can, of course, be generalized to any \ac{ZKPK} for discrete logarithms, 
for instance, CL04~\cite{CLsignatures}.

\begin{figure*}
  \centering
  \small
  \setlength{\ProtoArrowLength}{0.07\linewidth}
  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
    \(\HWprove[g, q, \alpha]\):
    & &
    \(\HWverify[g, q, A]\):
    \\
    \midrule

    \multicolumn{2}{l}{%
      Static \(\sk_P\in \ZZ_q, \sigma = (a, A, b, B, c)\)
    }
    & Static \(\pk = (\qCL, \gCL, \ggCL, e, \XCL, \YCL, \ZCL)\)
    \\

    \midrule
    \multicolumn{3}{c}{\textbf{Pre-setup key-agreement}} \\

    \(\xDH\rgets \ZZ_{\qDH}, \XDH\gets \gDH^{\xDH}, \XDHCL\gets \XDH^{\sk}\)
    & \(\ProtoSendRight{\XDH, \XDHCL}\)
    & \(\yDH\rgets \ZZ_{\qDH}\)
    \\

    \(k \gets \YDH^{\xDH}\)
    & \(\ProtoSendLeft{\YDH = \gDH^{\yDH}}\)
    & \(k \gets \XDH^{\yDH}\)
    \\

    \midrule
    \multicolumn{3}{c}{\textbf{Setup}} \\

    Load \(k\) into \(\UWBPR\)
    &
    & Load \(k\) into \(\UWBPR\)
    \\

    \(r_1, r_2\rgets \ZZ_{\qCL}\)
    &
    &
    \\

    \(\tilde a = a^{r_1},
      \tilde A = A^{r_1},
      \tilde b = b^{r_1},
      \tilde B = B^{r_1},
      \tilde c = (c^{r_1})^{r_2}\)
    & \(\ProtoSendRight{
        \tilde \sigma = (\tilde a, \tilde A, \tilde b, \tilde B, \tilde c)
      }\)
    &
    \\[0.5em]

    \(v_x = e(\XCL, \tilde a),
      v_{xy} = e(\XCL, \tilde b),
      V_{xy} = e(\XCL, \tilde B),
      v_s = e(\gCL, \tilde c)\)
    &
    & \(v_x = e(\XCL, \tilde a),
      v_{xy} = e(\XCL, \tilde b),
      V_{xy} = e(\XCL, \tilde B),
      v_s = e(\gCL, \tilde c)\)
    \\[0.5em]

    \(\rho\rgets \ZZ_q,
      \rhoDH \rgets \ZZ_{\qDH},
      \rhoCL_{\sk} \rgets \ZZ_{\qCL},
      \rhoCL_{r} \rgets \ZZ_{\qCL},
      \rhoCL_{r'} \rgets \ZZ_{\qCL}\)
    &
    &
    \\

    \(R\gets g^{\rho},
      \RDH\gets \gDH^{\rhoDH},
      \RDHCL\gets \XDH^{\rhoCL_{\sk}},
      \RCL\gets v_s^{\rhoCL_{r'}} v_{xy}^{\rhoCL_{\sk}} V_{xy}^{\rhoCL_r}\)
    & \(\ProtoSendRight{R, \RDH, \RDHCL, \RCL}\)
    &
    \\

    \(\forall i\in \{1, \dotsc, m\}\):
    & \(\ProtoSendLeft{c_1, \dotsc, c_k}\)
    & \(c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l\)
    \\

    \(s_i\gets \rho - c_i\alpha \pmod q\)
    &
    &
    \\

    \(\sDH_i\gets \rhoDH - c_i \xDH \pmod \qDH\)
    &
    &
    \\

    \(\sCL_i^{(r')}\gets \rhoCL_{r'} + c_i r' \pmod \qCL\)
    &
    &
    \\

    \(\sCL_i^{(\sk)}\gets \rhoCL_{\sk} - c_i \sk \pmod \qCL\)
    &
    &
    \\

    \(\sCL_i^{(r)}\gets \rhoCL_{r} - c_i r \pmod \qCL\)
    &
    &
    \\

    Fetch \(s_i, \sDH_i, \sCL_i^{(r')}, \sCL_i^{(\sk)}, \sCL_i^{(r)}\)
    & \(\ProtoSendRight{
      s_i, \sDH_i, \sCL_i^{(r')}, \sCL_i^{(\sk)}, \sCL_i^{(r)}}\)
    & Stop clock, record \(\Delta t\)
    \\

    % null
    &
    & Accept if \(\Delta t < t_{\max}\) and
    \\

    % null
    &
    & \(R = A^{c_i} g^{s_i}\),
    \\

    % null
    &
    & \(\RDH = \XDH^{c_i} \gDH^{\sDH_i}\),
    \\

    % null
    &
    & \(\RDHCL = \XDHCL^{c_i} \XDH^{\sCL_i^{(\sk)}}\),
    \\

    % null
    &
    & \(v_x^{c_i} \RCL =
          v_s^{\sCL_i^{(r')}} v_{xy}^{\sCL_i^{(\sk)}} V_{xy}^{\sCL_i^{(r)}}\),
    \\

    %
    &
    & \(e(\tilde a, \ZCL) = e(\gCL, \tilde A)\),
    \\

    %
    &
    & \(e(\tilde a, \YCL) = e(\gCL, \tilde b)\),
    \\

    %
    &
    & \(e(\tilde A, \YCL) = e(\gCL, \tilde B)\).
    \\

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSHW\) protocol instantiating 
    \(\PK[\alpha][A = g^\alpha]\).
    Each transmission (arrow in the diagram) uses \(\UWBPR\) (except in the 
    pre-setup phase).
    The protocol actually proves \(
      \PK[\alpha, \xDH, \sk, \sigma][
        A = g^\alpha \land
        \XDH = \gDH^{\xDH} \land
        \XDHCL = \XDH^{\sk} \land
        \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
      ].
    \)
    This is ties \(\xDH\), and consequently \(k\), to \(\sk_P\) and \(\alpha\).
    The protocol (setup, distance-bounding and verification phases) should be 
    repeated \(n\) times to achieve the desired soundness and distance-bounding 
    errors.
  }%
  \label{DBSHW-overview}
\end{figure*}

\paragraph*{One-time initialization}

The prover's \(\DBSHW\) device must be initialized with a (static) private 
key~\(\sk_P\) and a signature~\(\sigma\) on that key by some \ac{CA} with 
public key~\(\pk\) and signing key~\(\sk\).
These are computed as follows~\cite[cf.][Sect.~4.2]{CLsignatures}.

We have public parameters \(\qCL, \gCL\in\GCL, \ggCL\in\GGCL, e\); where 
\(e\colon \GCL\times \GCL\to \GGCL\) is a bilinear map, \(\gCL\in \GCL\) and 
\(\ggCL\in \GGCL\) are generators of prime order \(\qCL\) (hence \(e(\gCL, 
\gCL) = \ggCL\)).

We let the \acg{CA} signing key be \[
  \sk = (\xCL, \yCL, \zCL)\rgets \ZZ_{\qCL}^3
\] and the public key be \[
  \pk = (\qCL, \gCL, \ggCL, e, \XCL, \YCL, \ZCL),
\] where \[
  \XCL = \gCL^{\xCL}, \quad
  \YCL = \gCL^{\yCL}, \quad
  \ZCL = \gCL^{\zCL}.
\]

The prover chooses \(\sk_P\rgets \ZZ_{\qCL}\) and computes a commitment \(M = 
\gCL^{\sk_P} Z^r\), where \(r\rgets \ZZ_{\qCL}\).
Now the prover convinces the \ac{CA} that he knows the key by running the 
following \ac{ZKPK} protocol: \(
  \PK[\sk_P, r][M = \gCL^{\sk_P} Z^r].
\)

Now the \ac{CA} computes the signature~\(\sigma = (a, A, b, B, c)\), where \[
  \alpha\rgets \ZZ_{\qCL}, \quad a\gets \gCL^\alpha, \quad
  A\gets \gCL^{\zCL}, \quad
  b\gets a^{\yCL}, \quad
  B\gets A^{\yCL}, \quad
  c\gets a^{\xCL} M^{\alpha \xCL \yCL}
\] and gives to the prover.

\paragraph*{Pre-setup key-agreement}

The pre-setup phase consists of a key agreement, the prover and verifier must 
agree on a shared key~\(k\) to use for the \(\UWBPR\) protocol on the physical 
layer.

To establish \(k\), we use the \ac{DHKE}.
The prover chooses \(\xDH \rgets \ZZ_{\qDH}\), the verifier chooses 
\(\yDH\rgets \ZZ_{\qDH}\) and they exchange \(\XDH = \gDH^{\xDH}, \YDH = 
\gDH^{\yDH}\) and both compute
\(k = \gDH^{\xDH \yDH}\), for some generator \(\gDH\) in \iac{DH} group of 
prime order \(\qDH\).
The prover also computes \(\XDHCL\rgets \XDH^{\sk}\) and sends to the verifier.

\paragraph*{Setup}

The setup phase is similar to \(\DBS\) (\cref{DB-Schnorr-UWB-figure}).
They use the agreed upon key~\(k = \gDH^{\xDH \yDH}\) as the key for 
\(\UWBPR\), instead of a static \(k\).
\(\DBS\) performs \(
  \PK[\alpha][A = g^\alpha]
\) (with a distance bound) whereas \(\DBSHW\) must perform \[
  \PK[\alpha, \xDH, \sk_P, \sigma][
    A = g^\alpha \land
    \XDH = \gDH^{\xDH} \land
    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
  ].
\] This means that the prover (and verifier) must prepare for the other proofs 
too.

The prover blinds the signature~\(\sigma\):
Choose \(r_1, r_2\rgets \ZZ_{\qCL}\) and compute \(\tilde \sigma = (\tilde a, 
\tilde A, \tilde b, \tilde B, \tilde c)\), where \[
  \tilde a = a^{r_1}, \quad
  \tilde A = A^{r_1}, \quad
  \tilde b = b^{r_1}, \quad
  \tilde B = B^{r_1}, \quad
  \tilde c = (c^{r_1})^{r_2}.
\]
The prover sends \(\tilde \sigma\) to the verifier.
Now, the prover and verifier each compute \[
  v_x\gets e(\XCL, \tilde a), \quad
  v_{xy}\gets e(\XCL, \tilde b), \quad
  V_{xy}\gets e(\XCL, \tilde B), \quad
  v_s\gets e(\gCL, \tilde c).
\]

The prover chooses \[
  \rho\rgets \ZZ_q, \quad
  \rhoDH\rgets \ZZ_{\qDH}, \quad
  \rhoCL_{\sk}\rgets \ZZ_{\qCL}, \quad
  \rhoCL_r\rgets \ZZ_{\qCL}, \quad
  \rhoCL_{r'}\rgets \ZZ_{\qCL}
\] computes \[
  R\gets g^\rho, \quad
  \RDH\gets \gDH^{\rhoDH}, \quad
  \RDHCL\gets \XDH^{\rhoCL_{\sk}}, \quad
  \RCL\gets v_s^{\rhoCL_{r'}} v_{xy}^{\rhoCL_{\sk}} V_{xy}^{\rhoCL_r}
\] and sends \(R, \RDH, \RCL\) to the verifier.

The verifier chooses \(m\) challenges of length \(l\), \(c_1\rgets \bin^l, 
\dotsc, c_m\rgets \bin^l\), and sends these to the prover.
The prover computes responses
\begin{multline*}
  s_i\gets \rho - c_i\alpha, \quad
  \sDH_i\gets \rhoDH - c_i \xDH, \\%\quad
  \sCL_i^{(r')}\gets \rhoCL_{r'} + c_i r', \quad
  \sCL_i^{(\sk)}\gets \rhoCL_{\sk} - c_i \sk, \quad
  \sCL_i^{(r)}\gets \rhoCL_r - c_i r
\end{multline*}
for \(i\in \{1, \dotsc, m\}\), where \(r' = r_2^{-1}\).

\paragraph*{Distance bounding}

The verifier decides which of the \(m\) challenges to use, \(i\rgets \{1, 
\dotsc, m\}\), sends its decision~\(i\) to the prover and starts its clock.
The prover instantly replies with the pre-computed \(s_i, \sDH_i, 
\sCL_i^{(r')}, \sCL_i^{(\sk)}, \sCL_i^{(r')}\).
Note that these values must be sent as a concatenation in \emph{one} \(\UWBPR\) 
reply.
The verifier stops the clock and records the round-trip time~\(\Delta t\).

\paragraph*{Verification}

The verifier checks that \[
  R = A^{c_i} g^{s_i}, \quad
  \RDH = \XDH^{c_i} g^{\sDH_i}, \quad
  \RDHCL = \XDHCL^{c_i} \XDH^{\sCL_i^{(\sk)}}, \quad
  v_x^{c_i} \RCL = v_s^{s_{r'}} v_{xy}^{s_{\sk_P}} V_{xy}^{s_r}
\] and that the round-trip time \(\Delta t < t_{\max}\) does not exceed the 
time-limit~\(t_{\max}\) (corresponding to the desired distance bound).
Finally, the verifier checks the validity of \(\tilde \sigma\): \[
  e(\tilde a, \ZCL) = e(\gCL, \tilde A), \quad
  e(\tilde a, \YCL) = e(\gCL, \tilde b), \quad
  e(\tilde A, \YCL) = e(\gCL, \tilde B).
\]

\subsection{Security analysis}

There are two questions we must answer about this protocol:
\begin{enumerate}
  \item\label{DBSHW-MITM} Can the adversary perform \iac{MITM} attack against 
    the \ac{DHKE}?
  \item\label{DBSHW-anon} Does \(\XDHCL\) break anonymity?
\end{enumerate}

To answer the first question,
by \textcite{Camenisch-phdthesis}, the above protocol is \iac{ZKPK}.
In the case of \iac{MITM}, the prover will run the protocol using \(\XDH\) and 
\(\sk\), while the verifier will use \(\XDH'\), possibly modified by the 
adversary.
The adversary's goal is to pass as knowing \(\sk\) and its signature (to 
impersonate real hardware).
The \(\sk\) must be the same \(\sk\) throughout the 
subproofs~\cite{Camenisch-phdthesis}.
In one subprotocol, the prover will prove knowledge of \(\XDH^{\sk}\).
If \(\XDH' \neq \XDH\) used by the verifier is wrong, then by soundness the 
proof will fail.

To answer the second question,
\(\XDHCL = \XDH^{\sk}\) is simply a representation of \(\sk\) in a randomly 
chosen base~\(\XDH\).
If an adversary can use this to tell one device from another, then the 
adversary can solve the \ac{DDH} problem.
Consider the following reduction.

Assume that \(\adv\) can tell \(\XDH^{\sk}\) from \(\XDH^{\sk'}\) with 
probability \(\frac{1}{2} + \epsilon\) (\ie \(\epsilon\) better than guessing).
We get the \ac{DDH} challenge tuple \(g, X = g^x, Y = g^y, Z = g^z\) and must 
decide if \(Z = g^{xy}\) or not.
Give \(g, R_i = g^{r_i}\) and \(X^{r_i}\) to \(\adv\), for \(1\leq i\leq n\).
Finally, give \(\adv\) the challenge \(g, Y, Z\).
If \(\adv\) recognizes \(Z\), then \(Z = g^{xy}\), and we will solve the 
\ac{DDH} with the same advantage \(\epsilon\).

>>>>

\section{Distance-bounding \aclp*{ZKPK} for discrete logarithms}%
\label{DB-Schnorr}

@@

We will provide two versions of the protocol.
In the first (\cref{DB-Schnorr-UWB}), we will assume that we can send as many 
bits in parallel as we like.
This is a reasonable assumption thanks to the results of \textcite{UWBPR}.

Next (\cref{DB-Schnorr-PKI}), we will provide \iac{PKI} construction to make 
the shared-key requirement of \textcite{UWBPR} more practical.
This would allow any two devices to run our protocol as long as they are both 
part of the \ac{PKI}.
We use the first version of our protocol to ensure correctness of the \ac{PKI}.

Finally (\cref{DB-Schnorr-nbit}), we provide a classical bit-by-bit version of 
our protocol.

\subsection{Reattempting a distance-bounding Schnorr protocol}%
\label{DB-Schnorr-UWB}

In this version, we assume that we can simply send as many bits in parallel as 
we like.
This allows us to keep the Schnorr protocol almost as is.

We present the protocol in \cref{DB-Schnorr-UWB-figure}.
The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.
%Let \(\UWBPR\) be the protocol of \textcite{UWBPR}.
%Further, let
%\(\UWBPRsend[_k][m]\) denote sending a message~\(m\) with the shared key~\(k\),
%\(m'\gets \UWBPRrecv_k\) denote receiving a message~\(m'\) with shared 
%key~\(k\) and finally
%\(\Delta t\gets \UWBPRtime\) denote the time between the last \(\UWBPRsend\) 
%and \(\UWBPRrecv\) operations.

\begin{figure*}
  \centering
  \small
  \setlength{\ProtoArrowLength}{0.07\linewidth}
  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[g, q, A]\):
    \\
    \midrule

@@

@@

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
    protocol instantiating \(\PK[\alpha][A = g^\alpha]\).
    The protocol should be repeated \(n\) times to achieve the desired 
    soundness and distance-bounding errors.
  }%
  \label{DB-Schnorr-UWB-figure}
\end{figure*}

@@

The intuition behind the protocol security is as follows.
The prover must know the responses for all challenges to successfully pass the 
\ac{DB} phase.
The reason for having several challenges but only one random nonce is that 
knowing at least two responses means learning the secret~\(\alpha\).
This gives us the incentives that prevent \ac{DBTF}.
(We also need it for \ac{DBMF} and \ac{DBDF}.)
Bundling the authentication into the distance-bounding phase (difference from 
Brands-Chaum) prevents \ac{DBDH}.

@@

By \cref{TaintedMF}, any relaying will be detected by the verifier.
This means that the adversary must use a different strategy.

\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \frac{1}{m^n}\), where \(m\) is as in 
  \cref{DB-Schnorr-UWB}.
\end{theorem}

@@

The protocol is \ac{DBTF} resistant.
Indeed, if the malicious prover gives more than one response to the accomplice, 
the accomplice can compute the secret key and, thus, impersonate forever.
And we show that any useful help will ensure this.

@@
